### 2024-10-26 paper/3-motivation.tex
Add code example

@@

It might be easy to understand how the \officialp{} explains the control flow
of WebAssembly, if we assume that a WebAssembly code is loaded on a memory and
a pc points to the instruction to execute.
To describe control flow, it uses a structure named \textit{block} which
consitutes of a instruction sequence.
When executing the instruction sequence inside the block, it can jump to the
starting point of the block or the end of the block.
For example, \cref{loop-fig} is the \officialp{} \texttt{loop} instruction.
It says that the continuation is the start of the loop and the information is
stored in a label, which is pushed in the stack when
entering the block.
\cref{br-fig} is a \texttt{br} instruction in the \officialp{}.
According to it, if the \texttt{br} instruction in the block is executed to
branch out the block, the label is popped in the stack and jumps to the
continuation of the label, which is the start of the loop instruction.

@@

However, rather than using the notion like pc, the \spectecp{} assumes that the
\red{machine} takes WebAssembly instructions one by one, and changes the
internal state accordingly.
This is because the \spectecp{} is generated automatically from the \red{dsl}
which doesn't model the pc.
As a result, rather than jump to the start of the loop, \spectecp{} stores the
\texttt{loop} instruction in the label, and executes it again if \texttt{br}
instruction is executed.

>>>>

It might be easy to understand how the \officialp{} explains the control flow
of WebAssembly, if we assume that a WebAssembly code is loaded on a memory and
a pc points to the instruction to execute.
To describe control flow, it uses a structure named \textit{block} which
consitutes of a instruction sequence.
When executing the instruction sequence inside the block, it can jump to the
starting point of the block or the end of the block.

\textbf{Example 1}
\begin{verbatim}
  // infinite loop
  (loop (result i32) (i32.const 42) (br 0) (unreachable) end)
\end{verbatim}

Example 1 is a WebAssembly code example that has a \texttt{loop} whose result
type is \texttt{i32} and has a block of three instructions: \texttt{i32.const},
\texttt{br}, \texttt{unreachable}.
\cref{loop-fig} is the \officialp{} of \texttt{loop} instruction.
It says that the continuation is the start of the loop, the information is
stored in a label, and it \textit{enters} the block with the label.
The term enter means that it pushes the label in the stack and makes pc points
to the first instruction in the block.
\texttt{i32.const} instruction is executed first, which just pushes the
value in the stack.
Then, \texttt{br} instruction is executed.
\cref{br-fig} is the \officialp{} of \texttt{br} instruction.
It pops the label from the stack, and makes pc points to the continuation of
the label, which is the start of the loop instruction.
As a result, the code example above is a infinite loop pushing a \texttt{i32}
value \texttt{42} infinitely.

@@

@@

However, the \spectecp{} assumes that the \red{machine} takes WebAssembly
instructions one by one, and changes the internal state accordingly without pc.
This is because the \spectecp{} is generated automatically from the \red{dsl}
which uses rewrite rule to describe WebAssembly semantics.
As a result, rather than jump to the start of the loop, \spectecp{} stores the
\texttt{loop} instruction itself in the label, and executes it again if the
\texttt{br} instruction is executed.
Not only that, it doesn't have block structure.
